Concurrent Programming in Harmony

### 2021-08-07 book/paper.tex
Latest

\autoref{fig:chain} shows an implemenation of chain replication.

>>>>

\autoref{fig:chain} shows an implemenation of chain replication.
The code starts \texttt{NREPLICAS} \texttt{replica} threads numbered
0 through $\mathtt{NREPLICAS} - 1$.  At least one of the replicas 
must be immortal---the code selects one of them although none of the
replicas is required to fail during execution.
Each replica maintains its history and a set of its predecessors.
It then loops until either it fails or it has applied all
\texttt{NOPS} operations to its history.
$\mathbf{choose}(\{ \mathit{immortal}, \texttt{True} \})$ can only
evalute to \texttt{False} in case $\textit{immortal}$ is false.
What it does within the loop depends on whether it is the head
(has no alive predecessors) or not.
Because failure detection is accurate, at most one replica can think
it is the head at any time.  Moreover, eventually, when it has
detected all its predecessors having failed, always some replica
thinks it is the head.

Messages have the format $(\mathit{source}, \mathit{payload})$,
where \textit{source} is the identifier of the replica that generated
the message and \textit{payload} has information about the state of
the replica.  The payload can take one of two forms.  The first is
\texttt{.crash}, indicating that the source of the message has
crashed.  The code models a replica crashing by that replica broadcasting
this message on the network.  The other form is a tuple
$(\mathit{index}, \mathit{operation})$, which means that the source
placed the given operation at the given index in its history.
